---
title: "mmse-map"
output:
  html_document:
    css: ~/GitHub/cognition-stress-activity/libs/css/sidebar.css
    keep_md: yes
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes

---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 5.5, 
  out.width = "550px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
C_echo <- TRUE
C_message<- FALSE
C_warning<- FALSE

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./sandbox/map/building-models/3-mmse-map-LH.R") 
```

```{r load-packages, echo=FALSE, message=C_message, warning=C_warning}
```

```{r load-sources, echo=FALSE, message=C_message, warning=C_warning}
```


```{r declare-globals, echo=FALSE, message=C_message, warning=C_warning}
```

```{r load-data, echo=FALSE, message=C_message, warning=C_warning}
```

```{r define-variables, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```
# **confound Variables initial equations**
```{r confound-equations, echo=C_echo, message=C_message, warning=C_warning, eval=T}
```

### full data set- confound models
```{r confound-full, echo=C_echo, message=C_message, warning=C_warning, eval=T}
```

### male- confound models
```{r confound-male, echo=C_echo, message=C_message, warning=C_warning, eval=T}
```

### female- confound models
```{r confound-female, echo=C_echo, message=C_message, warning=C_warning, eval=T}
```
## **in the whole data set and for males and females separately, the following are significant;  
time in study  
age at baseline  
time in study X age at baseline  
and education are  

time in study X education is not significant.  

# **raw physical activity**
```{r raw-PA-equation, echo=C_echo, message=C_message, warning=C_warning}
```

### full data set - Raw PA
```{r raw-full, echo=C_echo, message=C_message, warning=C_warning}
```

### males - Raw PA
```{r raw-male, echo=C_echo, message=C_message, warning=C_warning}
```

### females -Raw PA
```{r raw-female, echo=C_echo, message=C_message, warning=C_warning}
```

## ** Raw scores of Physical activity are sig in the full data set and for males and females separately. 
## **higher levels of PA are associated with higher mmse scores**

# **Between-and-within-effects**
### below are 2 outputs each for the full data set, males only and females only. One is just between person (BP) effects, the other includes BP and within person (WP) effects 
```{r bp-wp-equation, echo=C_echo, message=C_message, warning=C_warning}
```

```{r comments0, echo=FALSE, message=C_message, warning=C_warning}
```
### full- bp and wp
```{r bp-wp-full, echo=C, message=C_message, warning=C_warning}
```
### male -bp and wp
```{r bp-wp-male, echo=C, message=C_message, warning=C_warning}
```
### female - bp and wp
```{r bp-wp-female, echo=C_echo, message=C_message, warning=C_warning}
```

## **BP effects are only significant for males. When males average physical activity is average than the average male, they have higher mmse scores.** 
## **WP are NS across all 3 analyses. Thus, those who walk more than their average at a specific wave, also score higher on mmse at that time**

### ??Is this a function of time in study- i.e. people walk more than "usual" earlier in the study, therefore have higher mmse because they are younger- or is that controlled for by including the wave variable in the model first??


# **TVC-interaction**

```{r comments2, echo=FALSE, message=C_message, warning=C_warning}
```
### physical activity (TVC) interaction with time equation
```{r tvc-intxn-equation, echo=C_echo, message=C_message, warning=C_warning}
```

### full - tvc interaction
```{r tvc-intxn-full, echo=C_echo, message=C_message, warning=C_warning}
```
### male - tvc interaction
```{r tvc-intxn-male, echo=C_echo, message=C_message, warning=C_warning}
```
### female - tvc interaction
```{r tvc-intxn-female, echo=C_echo, message=C_message, warning=C_warning}
```

## **wp person PA X years in study** is sig. across all 3 analyses. The graph below helps to explain this interaction.
## Overtime, the effects of PA are more pronounced. specifically, exercising becomes increasingly important with age. With increasing age, if you walk more than your own average, you are expected to have higher mmse scores at that occasion.

# hypothetical graph
```{r set-up-graph, echo=FALSE, message=C_message, warning=C_warning}
```

```{r graph0, echo=C_echo, message=C_message, warning=C_warning}
```
# **TVC by age-at-visit interaction**
## Using age at visit as the outcome, we see the same effects as above 
```{r tvc-intxn-equation-age, echo=C_echo, message=C_message, warning=C_warning}
```

```{r tvc-intxn, echo=C_echo, message=C_message, warning=C_warning}
```

```{r tvc-intxn-graph, echo=FALSE, message=C_message, warning=C_warning}
```

```{r comments3, echo=FALSE, message=C_message, warning=C_warning}
```
# **Fluctuation in MMSE**

##Here, I explore the effects of using deviations from your average mmse score, to see if within person changes in PA also predict mmse changes at that occasion 
## ? mostly this was exploratory and I wanted to know if you think it makes sense ?? 
##In the following models, WP effects of PA are significant across all 3 analyses. Thus, those who walk more than usual, also have higher mmse scores than their average at that occasion. 
```{r mmse_wp_fluctuations, echo=FALSE, message=C_message, warning=C_warning}
```

```{r mmse_wp_full, echo=FALSE, message=C_message, warning=C_warning}
```

```{r mmse_wp_male, echo=FALSE, message=C_message, warning=C_warning}
```

```{r mmse_wp_female, echo=FALSE, message=C_message, warning=C_warning}
```

# **random effects**
## Here, I include the random effects of the within person PA variable.
### random effects equation
```{r Random-effects-equation, echo=C_echo, message=C_message, warning=C_warning}
```
### full- random effects 
```{r Random-effects-full, echo=C_echo, message=C_message, warning=C_warning}
```
### male - random effects 
```{r Random-effects-male, echo=C_echo, message=C_message, warning=C_warning}
```
### female - random effects 
```{r Random-effects-female, echo=C_echo, message=C_message, warning=C_warning}
```
## When the random effects are included, Males between person main effect of PA is no longer significant
##? I am struggling to understand why allowing the slope of PA for males to vary across people results in non-sig results, when this effect was sig. in the restricted slope model
##Moreover, WP effects are sig. across all 3 analyses. People vary in how much they fluctuate from their average over time, and this fluctuation is sig associated with mmse  
(??)Am I interpreting this right??

# ** allostatic load models**
```{r biomarker-models, echo=C_echo, message=C_message, warning=C_warning}
```
### full
```{r biomarker-full, echo=C_echo, message=C_message, warning=C_warning}
```
### male
```{r biomarker-male, echo=C_echo, message=C_message, warning=C_warning}
```
### female
```{r biomarker-female, echo=C_echo, message=C_message, warning=C_warning }
```
# **graph**
```{r graph-biomarker, echo=FALSE, message=C_message, warning=C_warning}
```
## The higher the Allostatic load composite score, the lower your mmse score across all 3 analyses 

# **AL score X physical Activity
```{r biomarker-interaction, echo=C_echo, message=C_message, warning=C_warning, eval=FALSE}
```
# *explore*
```{r PA-predicted-by-bio, echo=C_echo, message=C_message, warning=C_warning, eval=FALSE}
```

```{r transform, echo=C_echo, message=C_message, warning=C_warning}
```

## fluctuations in allostatic load score are not predcited by fluctuations in physical activity.
```{r PA_Within-predicted-by-bio_within, echo=C_echo, message=C_message, warning=C_warning}
```

```{r biomarker-interaction2, echo=C_echo, message=C_message, warning=C_warning}
```









