---
title: "dsb-map"
output:
  html_document:
    css: ~/GitHub/cognition-stress-activity/libs/css/sidebar.css
    keep_md: yes
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes

---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 5.5, 
  out.width = "550px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
C_echo <- TRUE
C_message<- FALSE
C_warning<- FALSE

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./sandbox/map/building-models/dsb-map-LH.R") 
```

```{r load-packages, echo=FALSE, message=C_message, warning=C_warning}
```

```{r load-sources, echo=FALSE, message=C_message, warning=C_warning}
```


```{r declare-globals, echo=FALSE, message=C_message, warning=C_warning}
```

```{r load-data, echo=FALSE, message=C_message, warning=C_warning}
```

```{r define-variables, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```
# **confound Variables initial equations**
```{r confound-equations, echo=C_echo, message=C_message, warning=C_warning, eval=T}
```

### full data set- confound models
```{r confound-full, echo=C_echo, message=C_message, warning=C_warning, eval=T}
```

### male- confound models
```{r confound-male, echo=C_echo, message=C_message, warning=C_warning, eval=T}
```

### female- confound models
```{r confound-female, echo=C_echo, message=C_message, warning=C_warning, eval=T}
```

# **raw physical activity**
```{r raw-PA-equation, echo=C_echo, message=C_message, warning=C_warning}
```

### full data set - Raw PA
```{r raw-full, echo=C_echo, message=C_message, warning=C_warning}
```

### males - Raw PA
```{r raw-male, echo=C_echo, message=C_message, warning=C_warning}
```

### females -Raw PA
```{r raw-female, echo=C_echo, message=C_message, warning=C_warning}
```



# **Between-and-within-effects**

```{r bp-wp-equation, echo=C_echo, message=C_message, warning=C_warning}
```

```{r comments0, echo=FALSE, message=C_message, warning=C_warning}
```
### full- bp and wp
```{r bp-wp-full, echo=C, message=C_message, warning=C_warning}
```
### male -bp and wp
```{r bp-wp-male, echo=C, message=C_message, warning=C_warning}
```
### female - bp and wp
```{r bp-wp-female, echo=C_echo, message=C_message, warning=C_warning}
```



# **TVC-interaction**

```{r comments2, echo=FALSE, message=C_message, warning=C_warning}
```
### physical activity (TVC) interaction with time equation
```{r tvc-intxn-equation, echo=C_echo, message=C_message, warning=C_warning}
```

### full - tvc interaction
```{r tvc-intxn-full, echo=C_echo, message=C_message, warning=C_warning}
```
### male - tvc interaction
```{r tvc-intxn-male, echo=C_echo, message=C_message, warning=C_warning}
```
### female - tvc interaction
```{r tvc-intxn-female, echo=C_echo, message=C_message, warning=C_warning}
```



# hypothetical graph
```{r set-up-graph, echo=FALSE, message=C_message, warning=C_warning}
```

```{r graph0, echo=C_echo, message=C_message, warning=C_warning}
```
# **TVC by age-at-visit interaction**

```{r tvc-intxn-equation-age, echo=C_echo, message=C_message, warning=C_warning}
```

```{r tvc-intxn, echo=C_echo, message=C_message, warning=C_warning}
```

```{r tvc-intxn-graph, echo=FALSE, message=C_message, warning=C_warning}
```

```{r comments3, echo=FALSE, message=C_message, warning=C_warning}
```
# **Fluctuation in MMSE**

##Here, I explore the effects of using deviations from your average mmse score, to see if within person changes in PA also predict mmse changes at that occasion 
 
```{r mmse_wp_fluctuations, echo=C_echo, message=C_message, warning=C_warning}
```

```{r mmse_wp_full, echo=C_echo, message=C_message, warning=C_warning}
```

```{r mmse_wp_male, echo=C_echo, message=C_message, warning=C_warning}
```

```{r mmse_wp_female, echo=C_echo, message=C_message, warning=C_warning}
```

# **random effects**
## Here, I include the random effects of the within person PA variable.
### random effects equation
```{r Random-effects-equation, echo=C_echo, message=C_message, warning=C_warning}
```
### full- random effects 
```{r Random-effects-full, echo=C_echo, message=C_message, warning=C_warning}
```
### male - random effects 
```{r Random-effects-male, echo=C_echo, message=C_message, warning=C_warning}
```
### female - random effects 
```{r Random-effects-female, echo=C_echo, message=C_message, warning=C_warning}
```
## When the random effects are included, Males between person main effect of PA is no longer significant
##? I am struggling to understand why allowing the slope of PA for males to vary across people results in non-sig results, when this effect was sig. in the restricted slope model
##Moreover, WP effects are sig. across all 3 analyses. People vary in how much they fluctuate from their average over time, and this fluctuation is sig associated with mmse  
(??)Am I interpreting this right??

# ** allostatic load models**
```{r biomarker-models, echo=C_echo, message=C_message, warning=C_warning}
```
### full
```{r biomarker-full, echo=C_echo, message=C_message, warning=C_warning}
```
### male
```{r biomarker-male, echo=C_echo, message=C_message, warning=C_warning}
```
### female
```{r biomarker-female, echo=C_echo, message=C_message, warning=C_warning }
```
# **graph**
```{r graph-biomarker, echo=FALSE, message=C_message, warning=C_warning}
```


# **AL score X physical Activity
```{r biomarker-interaction, echo=C_echo, message=C_message, warning=C_warning, eval=FALSE}
```
# *explore*
```{r PA-predicted-by-bio, echo=C_echo, message=C_message, warning=C_warning, eval=FALSE}
```

```{r transform, echo=C_echo, message=C_message, warning=C_warning}
```


```{r PA_Within-predicted-by-bio_within, echo=C_echo, message=C_message, warning=C_warning}
```


```{r biomarker-interaction2, echo=C_echo, message=C_message, warning=C_warning}
```








