---
title: "Exposition"
output:
  html_document:
    css: ~/GitHub/cognition-stress-activity/libs/css/sidebar.css
    keep_md: yes
    toc: yes
  pdf_document:
    toc: yes
  word_document:
    toc: yes
---

<!-- These two chunks should be added in the beginning of every .Rmd that you want to source an .R script -->
<!--  The 1st mandatory chunck  -->
<!--  Set the working directory to the repository's base directory -->
```{r, echo=F, message=F} 
#Don't combine this call with any other chunk 
# cat("Working directory: ", getwd()) # check where you are
  library(knitr)
# Rmd is in "./reports/reportA/reportA.Rmd", but now the root is "./"
  knitr::opts_knit$set(root.dir='../../') 
```

<!--  The 2nd mandatory chunck  -->
<!-- Set the report-wide options, and point to the external code file. -->
```{r set_options, echo=F}
# set options shared by all chunks
opts_chunk$set(
  results='show', 
  message = TRUE,
  comment = NA, 
  tidy = FALSE,
  fig.height = 4, 
  fig.width = 5.5, 
  out.width = "550px",
  fig.path = 'figure_rmd/',     
  dev = "png",
  dpi = 400
  # fig.path = 'figure_pdf/',     
  # dev = "pdf"#,
  # dev.args=list(pdf = list(colormodel = 'cmyk'))
)
C_echo <- TRUE
C_message<- FALSE
C_warning<- FALSE

echoChunks <- FALSE
options(width=120) #So the output is 50% wider than the default.
# connect to the file with the underlying R script  
read_chunk("./manipulation/map/3-exposition.R") 
```

```{r load-packages, echo=FALSE, message=C_message, warning=C_warning}
```

```{r load-sources, echo=FALSE, message=C_message, warning=C_warning}
```

```{r declare-globals, echo=FALSE, message=C_message, warning=C_warning}
```

```{r load-data, echo=FALSE, message=C_message, warning=C_warning}
```

```{r define-variables, echo=FALSE, message=C_message, warning=C_warning}
```
## Define Variables 

* phys_bl_bp = each persons baseline score - the baseline grand mean (between person baseline compare)  
* phys_bp_mean = the persons mean score across occasions - the grand mean  
* phys_bp_median = the persons median score across occasions - the grand median    
* phys_wp = that persons score at time j, minus their mean (deviations-from--own-mean)  
* mmse_wp = the persons mmse score at time j, minus their mean, so that a positive value indicated scores higehr then their mean   
* biomarker_high = indicates if the person's mean on that particular biomarker is above the 3rd quartile  

physical activity question: hours per week that the ppt. engages in 5 different categories  

## Tweak Data
```{r tweak-data, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```

```{r @knitr univariate-quality-check, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```

```{r BasicGraph1, echo=C_echo, message=C_message, warning=C_warning}
```

```{r BasicGraph2, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```

## Graphs  
## DSB over time
```{r dsb, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```

## MMSE over time
```{r mmse, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```

## PA over time
male walk more than the population average 
```{r PA, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```

## Between person effects
male walk more than the population average - but there are some males who are reporting really high PA across time,
this could be pulling their average up 
```{r PA_between, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```

## Within person effects
seems to be no difference between the sex's in deviations from their average exercise over time.Females 
may walk slightly more than their average over time
```{r PA_within, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```

```{r @knitr multi-variate-quality-check, echo=C_echo, message=C_message, warning=C_warning, eval=T}
```

```{r mv-raw, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```

```{r mv-bp, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```

```{r mv-wp, echo=FALSE, message=C_message, warning=C_warning, eval=T}
```

